\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2018-10-01 Documents/M1/Astronum_2018/manuscript.tex
Modified the bibliography

\begin{abstract}
We develop implicit-explicit (IMEX) schemes for neutrino transport though a background material in \texttt{thornado} code with two-moment method.
Two-moment method evolves the angular moments of a neutrino phase space distribution function and the moments have upper and lower bounds that introduced by Pauli's exclusion principle.
To ensure the scheme preserves these bounds, a algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
Severn algebraic closures are compared with these bounds and Cernohorsky \& Bludman closure which preserves the bounds is chosen for our IMEX schemes.
For the convex-invariant time integrator, two IMEX scheme named PD-ARSs have been proposed following the work in \cite{chu_2018}.
PD-ARS denotes convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy, high-order accuracy in the streaming limit, and works well in the diffusion limit.
The two PD-ARSs have second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore second-order and third-order accurate in the streaming limit.
The accuracy and convex-variance of PD-ARSs are demonstrated in the numerical tests with a first-order discontinuous Galerkin method for spatial discretization and a simple Lax-Friedrichs flux.

>>>>

\begin{abstract}
We develop implicit-explicit (IMEX) schemes for neutrino transport though a background material in \texttt{thornado} code with two-moment method.
Two-moment method evolves the angular moments of a neutrino phase space distribution function and the moments have upper and lower bounds that introduced by Pauli's exclusion principle.
To ensure the scheme preserves these bounds, a algebraic moment closure based on Fermi-Dirac statistics and a convex-invariant time integrator are demanded.
Severn algebraic closures are compared with these bounds and Cernohorsky \& Bludman closure\cite{cernohorskyBludman_1994} which preserves the bounds is chosen for our IMEX schemes.
For the convex-invariant time integrator, two IMEX scheme named PD-ARSs have been proposed following the work in \cite{chu_etal_2018}.
PD-ARS denotes convex-invariant IMEX Runge-Kutta scheme that has first-order accuracy, high-order accuracy in the streaming limit, and works well in the diffusion limit.
The two PD-ARSs have second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} as their explicit part, respectively, and therefore second-order and third-order accurate in the streaming limit.
The accuracy and convex-invariance of PD-ARSs are demonstrated in the numerical tests with a first-order discontinuous Galerkin method for spatial discretization and a simple Lax-Friedrichs flux.

### 2018-10-01 Documents/M1/Astronum_2018/sections/Conclusion.tex
Modified the bibliography

We have developed IMEX schemes for the two-moment neutrino transport in \texttt{thornado} code respecting Fermi-Dirac statistics.
The schemes employ algebraic closure based on Fermi-Dirac statistics, a first-order discontinuous Galerkin method, the simple Lax-Friedrichs flux with the convex-invariant time integrator to maintain point-wise realizability of the moments.
Since the realizability-preserving property is obtained from convexity of the realizable domain, it's possible to construct a scheme with high order DG method.
See \cite{chu_2018} for some examples with third-order DG method employed.

In the applications motivating this work, the neutrino distribution function can vary from 0 to 1, and we have considered the algebraic closure respecting Fermi-Dirac statistics for both low and high occupied condition.
Different values given by different algebraic closures were compared with the boundary values given by the Fermi-Dirac statistics at different occupation.
Among the algebraic closures we considered, Kershaw\cite{kershaw_1976}, Wilson\cite{wilson1975,leblanc1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 1\cite{janka1991} Janka 2\cite{janka1992} and Cernohorsky \& Bludman \cite{cernohorskyBludman_1994}, only Cernohorsky \& Bludman closure respecting Fermi-Dirac statistics for any occupancy.
And it is Cernohorsky \& Bludman closure that we employed in the numerical tests in Section~\ref{se:NumericalTests}.

Following the work we have done in \cite{chu_2018}, two PD-ARSs have been proposed.
The one with SSPRK2 is second-order and strong stability-preserving in the streaming limit while other with SSPRK3 is third-order.
Their properties, accuracy and convex-invariant, are demonstrated with numerical tests.

>>>>

We have developed IMEX schemes for the two-moment neutrino transport in \texttt{thornado} code respecting Fermi-Dirac statistics.
The schemes employ algebraic closure based on Fermi-Dirac statistics, a first-order discontinuous Galerkin method, the simple Lax-Friedrichs flux with the convex-invariant time integrator to maintain point-wise realizability of the moments.
Since the realizability-preserving property is obtained from convexity of the realizable domain, it's possible to construct a scheme with high order DG method.
See \cite{chu_etal_2018} for some examples with third-order DG method employed.

In the applications motivating this work, the neutrino distribution function can vary from 0 to 1, and we have considered the algebraic closure respecting Fermi-Dirac statistics for both low and high occupied condition.
Different values given by different algebraic closures were compared with the boundary values given by the Fermi-Dirac statistics at different occupation.
Among the algebraic closures we considered, Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblanc_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 1\cite{janka_1991} Janka 2\cite{janka_1992} and Cernohorsky \& Bludman \cite{cernohorskyBludman_1994}, only Cernohorsky \& Bludman closure respecting Fermi-Dirac statistics for any occupancy.
And it is Cernohorsky \& Bludman closure that we employed in the numerical tests in Section~\ref{se:NumericalTests}.

Following the work we have done in \cite{chu_etal_2018}, two PD-ARSs have been proposed.
The one with SSPRK2 is second-order and strong stability-preserving in the streaming limit while other with SSPRK3 is third-order.
Their properties, accuracy and convex-invariant, are demonstrated with numerical tests.

### 2018-10-01 Documents/M1/Astronum_2018/sections/Numerical.tex
Modified the bibliography

In this section we present the numerical results obtained with the PD-ARS schemes provided in this paper.
The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in various regimes.
The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the realizability-preserving of PD-ARSs scheme.
All the tests in this subsection were applied with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $.
\subsection{Accuracy Tests}
\label{se: Accuracy Tests}
To compare the accuracy of the IMEX scheme, we applied our PDARSs and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
All the tests in this subsection were applied with the maximum entropy closure in the low occupancy limit.
In the streaming test, the second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} , (SSPRK2 and SSPRK3, respectively) are also applied to serve as an reference.
More information and the definition of the absolute error and the relative error can be found in \cite{chu_2018}.

\subsubsection{Sine Wave Streaming}
This test involves the streaming part only: the collision term is turned off. 
A periodic domain $D$ was applied and the initial condition is given by...
More information can be found in \cite{chu_2018}.
In Figure ~\ref{fig: SineWaveStreaming}, the absolute error for the number density is plotted versus the number of elements $N$.
Errors obtained with SSPRK3 and PD-ARS with SSPRK3 decrease as $N^{-3}$ as expected.
All the other schemes have errors decreases as $N^{-2}$.
In the streaming limit, PD-ARSs degenerate to their explicit part, SSPRK2 and SSPRK3, respectively.
Hence, errors of PD-ARS and SSPRKs are indistinguishable on the plot.
Among the second-order schemes, SSP2332 has the smallest error.
\begin{figure}[h]
  \centering
    \includegraphics[width=0.6\textwidth]{figures/SineWaveStreaming}
   \caption{Absolute error versus number of elements $N$ for the streaming sine wave test.  Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), SSP2332 (green crossing), PD-ARS with SSPRK2 (light red circles) and PD-ARS with SSPRK2 (light red hexagram). Black dash-dot reference lines are proportional to $N^{-1}$ (top), $N^{-2}$ (middle), and $N^{-3}$ (bottom), respectively.}
   \label{fig: SineWaveStreaming}
\end{figure}

\subsubsection{Sine Wave Damping}
This test is adapted from \cite{skinnerOstriker_2013}.
Figure~\ref{fig:SineWaveDamping} shows the numerical result of sine wave damping test.
See \cite{chu_2018} for more information about the test setting.
SSP2332 as a second-order scheme display second order convergence rate.
PD-ARSs convergent in first order, as a price paid for realizability-preserving.
\begin{figure}[h]
  \centering
    \includegraphics[width=0.7\textwidth]{figures/SineWaveDamping}
   \caption{Relative error versus number of elements $N$ for the damping sine wave test. Results for different values of the absorption opacity $\sigma_{\Ab}$, employing various IMEX time stepping schemes, are compared.  Errors for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.  The IMEX schemes employed are SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).  Black dash-dot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
  \label{fig:SineWaveDamping}
\end{figure}

\subsubsection{Sine Wave Diffusion}
The last test with known smooth solution is sine wave diffusion test.
It is adopted from \cite{radice_etal_2013}.
See \cite{chu_2018} for more information about the test setting.
Figure~\ref{fig:SineWaveDiffusionJ} shows the numerical result.
SSP2332 and PD-ARSs display third-order accuracy for the number density $\cJ$ and second-oder accuracy for $\cH_{x}$ and their errors are difficult to distinguish.
PD-ARS with SSP2332 behaviors as good as SSP2332 in the diffusion region but requires 1/3 less implicit solver.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionJ}
    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionH}
  \end{tabular}
   \caption{Absolute error for the number density $\cJ$ (left) and the number flux $\cH_{x}$ (right) versus number of elements for the sine wave diffusion test.  Results with different values of the scattering opacity $\sigma_{\Scatt}$, employing different IMEX schemes, are compared.  Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.  The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram). Black dash-dot on the left plot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively. Black dash-dot on the right plot reference lines are proportional to $N^{-2}$ .}
   \label{fig:SineWaveDiffusionJ}
\end{figure}

>>>>

In this section we present the numerical results obtained with the PD-ARS schemes provided in this paper.
The tests in Section \ref{se: Accuracy Tests} are designed to compare the accuracy of the schemes in various regimes.
The test in Section \ref{se: Neutrino Stationary State Test} demonstrates the realizability-preserving of PD-ARSs scheme.
All the tests in this subsection were applied with third-order accurate spatial discretization (polynomials of degree $k=2$) and time step $\dt = 0.1 \times \dx $.
\subsection{Accuracy Tests}
\label{se: Accuracy Tests}
To compare the accuracy of the IMEX scheme, we applied our PDARSs and Pareschi \& Russo \cite{pareschiRusso_2005} (SSP2332) scheme to some smooth problems in streaming, absorption, ans scattering dominated regimes in one spatial dimension.
All the tests in this subsection were applied with the maximum entropy closure in the low occupancy limit.
In the streaming test, the second-order and third-order accurate explicit strong stability-preserving Runge-Kutta methods\cite{gottlieb_etal_2001} , (SSPRK2 and SSPRK3, respectively) are also applied to serve as an reference.
More information and the definition of the absolute error and the relative error can be found in \cite{chu_etal_2018}.

\subsubsection{Sine Wave Streaming}
This test involves the streaming part only: the collision term is turned off. 
A periodic domain $D$ was applied and the initial condition is given by...
More information can be found in \cite{chu_etal_2018}.
In Figure ~\ref{fig: SineWaveStreaming}, the absolute error for the number density is plotted versus the number of elements $N$.
Errors obtained with SSPRK3 and PD-ARS with SSPRK3 decrease as $N^{-3}$ as expected.
All the other schemes have errors decreases as $N^{-2}$.
In the streaming limit, PD-ARSs degenerate to their explicit part, SSPRK2 and SSPRK3, respectively.
Hence, errors of PD-ARS and SSPRKs are indistinguishable on the plot.
Among the second-order schemes, SSP2332 has the smallest error.
\begin{figure}[h]
  \centering
    \includegraphics[width=0.6\textwidth]{figures/SineWaveStreaming}
   \caption{Absolute error versus number of elements $N$ for the streaming sine wave test.  Results employing various time stepping schemes are compared: SSPRK2 (cyan triangles pointing up), SSPRK3 (cyan triangles pointing down), SSP2332 (green crossing), PD-ARS with SSPRK2 (light red circles) and PD-ARS with SSPRK2 (light red hexagram). Black dash-dot reference lines are proportional to $N^{-1}$ (top), $N^{-2}$ (middle), and $N^{-3}$ (bottom), respectively.}
   \label{fig: SineWaveStreaming}
\end{figure}

\subsubsection{Sine Wave Damping}
This test is adapted from \cite{skinnerOstriker_2013}.
Figure~\ref{fig:SineWaveDamping} shows the numerical result of sine wave damping test.
See \cite{chu_etal_2018} for more information about the test setting.
SSP2332 as a second-order scheme display second order convergence rate.
PD-ARSs convergent in first order, as a price paid for realizability-preserving.
\begin{figure}[h]
  \centering
    \includegraphics[width=0.7\textwidth]{figures/SineWaveDamping}
   \caption{Relative error versus number of elements $N$ for the damping sine wave test. Results for different values of the absorption opacity $\sigma_{\Ab}$, employing various IMEX time stepping schemes, are compared.  Errors for $\sigma_{\Ab}=0.1$, $1$, and $10$ are plotted with red, green, and blue lines, respectively.  The IMEX schemes employed are SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram).  Black dash-dot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively.}
  \label{fig:SineWaveDamping}
\end{figure}

\subsubsection{Sine Wave Diffusion}
The last test with known smooth solution is sine wave diffusion test.
It is adopted from \cite{radice_etal_2013}.
See \cite{chu_etal_2018} for more information about the test setting.
Figure~\ref{fig:SineWaveDiffusionJ} shows the numerical result.
SSP2332 and PD-ARSs display third-order accuracy for the number density $\cJ$ and second-oder accuracy for $\cH_{x}$ and their errors are difficult to distinguish.
PD-ARS with SSP2332 behaviors as good as SSP2332 in the diffusion region but requires 1/3 less implicit solver.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionJ}
    \includegraphics[width=0.5\textwidth]{figures/SineWaveDiffusionH}
  \end{tabular}
   \caption{Absolute error for the number density $\cJ$ (left) and the number flux $\cH_{x}$ (right) versus number of elements for the sine wave diffusion test.  Results with different values of the scattering opacity $\sigma_{\Scatt}$, employing different IMEX schemes, are compared.  Errors with $\sigma_{\Scatt}=10^{2}$, $10^{3}$, and $10^{4}$ are plotted with red, green, and blue lines, respectively.  The IMEX schemes employed are:  SSP2332 ($+$), PD-ARS with SSPRK2 (circles) and PD-ARS with SSPRK3 (hexagram). Black dash-dot on the left plot reference lines are proportional to $N^{-1}$ (top) and $N^{-2}$ (bottom), respectively. Black dash-dot on the right plot reference lines are proportional to $N^{-2}$ .}
   \label{fig:SineWaveDiffusionJ}
\end{figure}

### 2018-10-01 Documents/M1/Astronum_2018/sections/SpacialDiscretization.tex
Modified the bibliography

Divide the spatial domain $D$ into $N$ cells and denote the cell as $I_{i}$ with $i = 1,\ldots,N$, so that
\begin{equation*}
D = \cup_{i = 1}^{N} I_{i}.
\end{equation*}
Each of the cell has a volume/length of $\dx$.
Then we have cell average moment:
\begin{equation}
\bcM_{i} = \dfrac{1}{\dx} \int_{I_i}\bcM dx.
\end{equation}
Integrate Eq.~\eqref{eq:momentEquations} for each cell $I_{i}$ to have
\begin{equation}
\dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{\dx} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
\end{equation}
where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the integrated collision term.
In this paper we use the simple Lax-Friedrichs flux that given by
\begin{equation}
  \widehat{\bcF}_{LF}(\vect{\cM}_{a},\vect{\cM}_{b})
  =\f{1}{2}\,\big(\,\bcF(\vect{\cM}_{a})+\bcF(\vect{\cM}_{b})-(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big).
\end{equation}
Therefore, by treating the flux term explicitly and the collision term implicitly, we have
\begin{align*}
\bcM_{i}^{n+1} = \widetilde{\bcM}^{n}_{i} + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i})
\end{align*}
with
\begin{align*}
\widetilde{\bcM}^{n}_{i} 
& = \bcM_{i}^{n} - \dfrac{\dt}{\dx} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right)\nonumber \\
& = (1-\beta)\bcM_{i}^{n} + \beta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right]
\end{align*}
where $\beta := \dfrac{\dt}{\dx}$.
Assume $\bcM_{i}^{n}$ is realizable for all $i$. 
Lemma 3 in \cite{chu_2018} says $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.
Substitute the Lax-Friedrichs flux formula in and $\widetilde{\bcM}^{n}_{i}$ becomes a convex combination of $\bcM_{i}^{n}$ and the square bracket term if $\beta \in [0,1]$.
So it is realizable if $\beta \in [0,1]$ and the square bracket term is realizable.
Given by Lemma 2 in \cite{chu_2018}, the square bracket term is realizable.
Therefore, $\bcM^{n+1}_{i}$ remains realizable given $\beta \in [0,1]$.
Note that $\beta \in [0,1]$ is also the CFL condition of the Forward-Euler method employing on a transport only Boltzmann equation.

>>>>

Divide the spatial domain $D$ into $N$ cells and denote the cell as $I_{i}$ with $i = 1,\ldots,N$, so that
\begin{equation*}
D = \cup_{i = 1}^{N} I_{i}.
\end{equation*}
Each of the cell has a volume/length of $\dx$.
Then we have cell average moment:
\begin{equation}
\bcM_{i} = \dfrac{1}{\dx} \int_{I_i}\bcM dx.
\end{equation}
Integrate Eq.~\eqref{eq:momentEquations} for each cell $I_{i}$ to have
\begin{equation}
\dfrac{d \bcM_{i}}{d t} = - \dfrac{1}{\dx} \left( \widehat{\bcF}(\bcM_{i},\bcM_{i+1}) -  \widehat{\bcF}(\bcM_{i-1},\bcM_{i})\right) + \f{1}{\tau}\,\cC(\bcM_{i}),
\end{equation}
where $\widehat{\bcF}(\vect{\cM}_{a},\vect{\cM}_{b})$ is numerical flux and $\f{1}{\tau}\,\cC(\bcM_{i})$ is the integrated collision term.
In this paper we use the simple Lax-Friedrichs flux that given by
\begin{equation}
  \widehat{\bcF}_{LF}(\vect{\cM}_{a},\vect{\cM}_{b})
  =\f{1}{2}\,\big(\,\bcF(\vect{\cM}_{a})+\bcF(\vect{\cM}_{b})-(\,\vect{\cM}_{b}-\vect{\cM}_{a}\,)\,\big).
\end{equation}
Therefore, by treating the flux term explicitly and the collision term implicitly, we have
\begin{align*}
\bcM_{i}^{n+1} = \widetilde{\bcM}^{n}_{i} + \f{\dt}{\tau}\,\cC(\bcM^{n+1}_{i})
\end{align*}
with
\begin{align*}
\widetilde{\bcM}^{n}_{i} 
& = \bcM_{i}^{n} - \dfrac{\dt}{\dx} \left( \widehat{\bcF}(\bcM^{n}_{i},\bcM^{n}_{i+1}) -  \widehat{\bcF}(\bcM^{n}_{i-1},\bcM^{n}_{i})\right)\nonumber \\
& = (1-\beta)\bcM_{i}^{n} + \beta\left[ \f{1}{2}\left( \bcM^{n}_{i+1}-\bcF(\bcM^{n}_{i+1})\right)  + \f{1}{2}\left( \bcM^{n}_{i-1}+\bcF(\bcM^{n}_{i-1})\right)\right]
\end{align*}
where $\beta := \dfrac{\dt}{\dx}$.
Assume $\bcM_{i}^{n}$ is realizable for all $i$. 
Lemma 3 in \cite{chu_etal_2018} says $\bcM^{n+1}_{i}$ remains realizable given $\f{\dt}{\tau} > 0$ and $\widetilde{\bcM}^{n}_{i}$ is realizable.
Substitute the Lax-Friedrichs flux formula in and $\widetilde{\bcM}^{n}_{i}$ becomes a convex combination of $\bcM_{i}^{n}$ and the square bracket term if $\beta \in [0,1]$.
So it is realizable if $\beta \in [0,1]$ and the square bracket term is realizable.
Given by Lemma 2 in \cite{chu_etal_2018}, the square bracket term is realizable.
Therefore, $\bcM^{n+1}_{i}$ remains realizable given $\beta \in [0,1]$.
Note that $\beta \in [0,1]$ is also the CFL condition of the Forward-Euler method employing on a transport only Boltzmann equation.

### 2018-10-01 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Updated the introduction section.
Modified the two-moment method section.
Modified the bibliography

\subsection{Constraint-Preserving Implicit-Explicit Scheme}
The problem left for constructing a constraint-preserving IMEX is finding the conditions $(\tilde{a}_{ij})$, $(a_{ij})$, $\tilde{w}_{i}$ and $w_{i}$ need to satisfied and giving their possible values.
As Hu et al. did in their paper \cite{hu_etal_2018}, the stage values in Eq.~\eqref{imexStages} can be rewritten to
\begin{equation}
  \vect{u}^{(i)}
  =\sum_{j=0}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big]
  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}),\quad i=1,\ldots,s,
  \label{eq:imexStagesRewrite}
\end{equation}
It can be proved \cite{chu_2018} that the conditions we need for constraint-preserving IMEX is:
\begin{enumerate}
    \item Consistency of the implicit coefficients
    \begin{equation}
      \sum_{i=1}^{s}w_{i}=1.
    \end{equation}
    \item Second-order accuracy in the streaming limit; i.e., satisfies \begin{equation}
      \sum_{i=1}^{s}\tilde{w}_{i}=1
      \quad\text{and}\quad
      \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2},
      \label{eq:orderConditionsEx}
    \end{equation}
    \item Convex-invariant; i.e. satisfies 
    \begin{align}
      &a_{ii}>0, \quad c_{i0},\tilde{c}_{i0}\ge0, \quad \text{for} \quad i=2,\ldots,s, \nonumber \\
      &\text{and} \quad c_{ij},\tilde{c}_{ij}\ge0, \quad \text{for} \quad i=3,\ldots,s, \quad\text{and}\quad j=2,\ldots,i-1.  
    \end{align}
    with $\sum_{j=0}^{i-1}c_{ij}=1$, for $i=1,\ldots,s$, and $c_{\Sch}=\min_{\substack{i = 2,\ldots,s \\ 
                  j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.
    \item Well-behaved in the diffusion limit; i.e., satisfies \begin{equation}
      \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s.
      \label{eq:diffusionCondition}
    \end{equation}
    \item Less than four stages ($s\le3$).
    \item Globally stiffly accurate (GSA): $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$.
\end{enumerate}  
We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{Chu_2018})
We give two optimized PD-ARS scheme here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. They have $2$-nd order and $3$-rd order accuracy in the streaming limit, respectively.
\subsubsection{PD-ARS with SSPRK2}
The explicit part of this IMEX scheme is SSPRK2.
\begin{equation}
  \begin{array}{c | c c c}
  	0 & 0   & 0 & 0 \\
  	1 & 1   & 0 & 0 \\
  	1 & 1/2 & 1/2 & 0 \\ \hline
  	  & 1/2 & 1/2 & 0
  \end{array}
  \qquad
  \begin{array}{c | c c c}
  	0 & 0 & 0            & 0            \\
  	1 & 0 & 1            & 0            \\
  	1 & 0 & 1/2-\epsilon & 1/2+\epsilon \\ \hline
  	  & 0 & 1/2-\epsilon & 1/2+\epsilon
  \end{array}
\end{equation}

@@

\begin{equation}
  \begin{array}{c | c c c c}
  	    &     &     &     &  \\
  	 1  & 1   &     &     &  \\
  	1/2 & 1/4 & 1/4 &  \\
  	 1  & 1/6 & 1/6 & 2/3 &  \\ \hline
  	    & 1/6 & 1/6 & 2/3 &
  \end{array}
  \qquad
  \begin{array}{c | c c c c}
  	0 & 0 & 0            & 0            \\
  	1 & 0 & 1            & 0            \\
  	1/2 & 0 & 1/4 & 1/4 \\ 
  	1 & 0 & 1/6-\epsilon^2 /4 & 1/6-\epsilon/4 & 2/3+\epsilon(1+\epsilon)/4\\\hline
  	  & 0 & 1/6-\epsilon^2 /4 & 1/6-\epsilon/4 & 2/3+\epsilon(1+\epsilon)/4
  \end{array}
\end{equation}
For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 3\epsilon/2$ with $\epsilon \rightarrow 0^{+}$.

>>>>

\subsection{Constraint-Preserving Implicit-Explicit Scheme}
The problem left for constructing a constraint-preserving IMEX is finding the conditions $(\tilde{a}_{ij})$, $(a_{ij})$, $\tilde{w}_{i}$ and $w_{i}$ need to satisfied and giving their possible values.
As Hu et al. did in their paper \cite{hu_etal_2018}, the stage values in Eq.~\eqref{imexStages} can be rewritten to
\begin{equation}
  \vect{u}^{(i)}
  =\sum_{j=0}^{i-1}c_{ij}\Big[\,\vect{u}^{(j)}+\hat{c}_{ij}\,\dt\,\vect{\cT}(\vect{u}^{(j)})\,\Big]
  +a_{ii}\,\dt\,\f{1}{\tau}\,\vect{\cQ}(\vect{u}^{(i)}),\quad i=1,\ldots,s,
  \label{eq:imexStagesRewrite}
\end{equation}
It can be proved \cite{chu_etal_2018} that the conditions we need for constraint-preserving IMEX is:
\begin{enumerate}
    \item Consistency of the implicit coefficients
    \begin{equation}
      \sum_{i=1}^{s}w_{i}=1.
    \end{equation}
    \item Second-order accuracy in the streaming limit; i.e., satisfies \begin{equation}
      \sum_{i=1}^{s}\tilde{w}_{i}=1
      \quad\text{and}\quad
      \sum_{i=1}^{s}\tilde{w}_{i}\,\tilde{c}_{i}=\f{1}{2},
      \label{eq:orderConditionsEx}
    \end{equation}
    \item Convex-invariant; i.e. satisfies 
    \begin{align}
      &a_{ii}>0, \quad c_{i0},\tilde{c}_{i0}\ge0, \quad \text{for} \quad i=2,\ldots,s, \nonumber \\
      &\text{and} \quad c_{ij},\tilde{c}_{ij}\ge0, \quad \text{for} \quad i=3,\ldots,s, \quad\text{and}\quad j=2,\ldots,i-1.  
    \end{align}
    with $\sum_{j=0}^{i-1}c_{ij}=1$, for $i=1,\ldots,s$, and $c_{\Sch}=\min_{\substack{i = 2,\ldots,s \\ 
                  j = 0,2,\ldots,i-1}}\,\f{1}{\hat{c}_{ij}}>0$.
    \item Well-behaved in the diffusion limit; i.e., satisfies \begin{equation}
      \vect{e}_{i}^{T}A^{-1}\tilde{A}\,\vect{e} = 1, \quad i=2,\ldots,s.
      \label{eq:diffusionCondition}
    \end{equation}
    \item Less than four stages ($s\le3$).
    \item Globally stiffly accurate (GSA): $a_{si}=w_{i}$ and $\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s$.
\end{enumerate}  
We call the IMEX scheme satisfying the above conditions {PD-ARS}. (Definition 3 in \cite{chu_etal_2018})
We give two optimized PD-ARS scheme here: PD-ARS with SSPRK2 and  PD-ARS with SSPRK3. 
They have $2$-nd order and $3$-rd order accuracy in the streaming limit, respectively.
\subsubsection{PD-ARS with SSPRK2}
The explicit part of this IMEX scheme is SSPRK2.
\begin{equation}
  \begin{array}{c | c c c}
  	0 & 0   & 0 & 0 \\
  	1 & 1   & 0 & 0 \\
  	1 & 1/2 & 1/2 & 0 \\ \hline
  	  & 1/2 & 1/2 & 0
  \end{array}
  \qquad
  \begin{array}{c | c c c}
  	0 & 0 & 0            & 0            \\
  	1 & 0 & 1            & 0            \\
  	1 & 0 & 1/2-\epsilon & 1/2+\epsilon \\ \hline
  	  & 0 & 1/2-\epsilon & 1/2+\epsilon
  \end{array}
\end{equation}

@@

\begin{equation}
  \begin{array}{c | c c c c}
  	    &     &     &     &  \\
  	 1  & 1   &     &     &  \\
  	1/2 & 1/4 & 1/4 &  \\
  	 1  & 1/6 & 1/6 & 2/3 &  \\ \hline
  	    & 1/6 & 1/6 & 2/3 &
  \end{array}
  \qquad
  \begin{array}{c | c c c c}
  	0 & 0 & 0            & 0            \\
  	1 & 0 & 1            & 0            \\
  	1/2 & 0 & 1/4 & 1/4 \\ 
  	1 & 0 & 1/6-\epsilon^2 /4 & 1/6-\epsilon/4 & 2/3+\epsilon(1+\epsilon)/4\\\hline
  	  & 0 & 1/6-\epsilon^2 /4 & 1/6-\epsilon/4 & 2/3+\epsilon(1+\epsilon)/4
  \end{array}
\end{equation}
For these schemes, $c_{\mbox{\tiny Sch}}= 1 - 3\epsilon/2$ with $\epsilon \in [0,2/3)$. (\rc{Other forms})
